Modelling long-term effects of management strategies in mixed fisheries

### 2019-04-11 doc/MSE_MAR_18.tex
fixed a few typos

Meanwhile, when constraining both species, the production potential of both stocks was maintained, that is to say the yield curves were unchanged. The quota constraints were met by a reduction in fishing effort (Fig. \ref{f:effort}). as predicted in general terms by \cite{Ulrich2017}. This led to a reduction in fishing cost and an increase in net revenue over the mid-term because biomasses and yields increased. However, individual quota cobined with the stochastic fisheries catches resulted in lower than intended exploitation rates. The TACs were set so that the total TACs corresponded to the harvest rate that resulted in maximum sustainable yields. The TACs were divided in individual quotas for each fishing vessel. The lower than intended harvest rates were caused by the fact that despite their planning, fishers often exhausted one of the quotas before the other. If discarding is not allowed, then individual fishers must then stop fishing. At the population levels of the two species this resulted in overal cacthes that were lower than the TACs. Such lack of achieving MSY in mixed fisheries with multiple single-species quota has been described elsewhere \cite{Kempf2016, Rindorf2017, Hilborn2015}, but is generall attributed to differences in life-histories among fished species. In this study, the discrepancy between the intended annual quotas at MSY and realized catches is caused only by schochasticity in the system. This stochasticy in catch rates is observed in most fisheries \cite{Sampson1988, VanOostenbrugge2004, Smith1980, Bernasconi2015}. It is caused by the complex migration biology and the effects of environmental factors on fish behaviour. A well functioning quota market would allow vessels to swap excess quota for constraining and thus bring realized catches closer to quotas.

In the case study explored here, setting quotas based on MSY for all species resulted in mixed fisheries that were economically more viable in the long run compared to the unconstrained cased. It should be noted that this particular result may not hold true for mixed fisheries with unavoidable catches or bycatches of very low productive species. Fishing those species at their MSY levels would probably constrain effort to such an extent tat the net revenue will be reduced in the long-term \cite{Prellezo2016a,  Rindorf2017}.

The model aimed to evaluate the biological and economic effects of adopting a major policy change such as the CFP \cite{CFP2013}. Starting from an overfished mixed fishery under open access conditions but with a landing obligation, the response of individual effort allocation and the interannual population dynamics are explicitly modeled, while adopting MSY objectives. The analysis extended earlier approaches that used short-term state-dependent decision-making models (e.g. \cite{Alzorriz2018, Batsleer2016, Poos2010}) by including interannual population dynamics of fish stocks, and a management procedure that mimics the decisions of a management system. Such an MSE framework was thought of as a minimum realistic model \cite{Kell2007, Punt1995}. To keep the outcomes of the model simple, and to show the implications of the fishing effort allocation, the two fish populations modelled here are exactly the same apart from their spatial distribution difference (Fig. \ref{f:distribution}). As a result, if the landing obligation changes selectivity patterns in the short-term as predicted in \cite{Alzorriz2018, Batsleer2016}, the present MSE modeling approach allows the evaluation on the reference points for sustainable exploitation in longer terms by explicitly modelling how changes in exploitation rates impact fish populations and yields.

The forecasted effects of fisheries management in mixed fisheries result from spatial heterogeneity in resources and fishers adaptive behaviour. This emphasizes that human behaviour and decision-making are intrinsic parts of conservation and natural resource management and the need for incorporating detailed fishing dynamics in management strategy evaluation. Historically, the focus of management strategy evaluation has been primarily on population dynamics in single and multispecies fisheries \cite{Butterworth2007, Dichmont2006b, Punt1999, Punt2009, Smith1999, Punt2016}. Explicitly incorporating direct effects of human behaviour of those who harvest stocks is equally important \cite{Fulton2011,Milner-Gulland2012, Link2017}, but relatively few studies have attempted this \cite{Andersen2010, Ono2018, Simons2015a}. Our MSE that links a dynamic state variable model for fisher behavior to a multi-species age structured model provides an alternative to those approaches.

The complexity of adding fishers behaviour in a minimum realistic model of mixed fisheries in an MSE framework requires making several simplifying assumptions. The details and possible consequences of these assumptions have been discussed in eg. \cite{Alzorriz2018}, and include full compliance of fishers with the discarding policy, absence of a quota market, monthly choices on fishing, and a lack of interference competition among fishers. Also, the utility function only comprises of decisions based on annual net revenues, ommitting any social dynamics or tradition. These social dynamics and traditions are potentially important \cite{Girardin2017, Schluter2012}, and could be incorporated in future applications. Important assumptions about the dynamics of the population dynamics included negligible natural mortality, constant recruitment, constant growth, and constant migration.

In the study, the fishes were not allowed to discard, complying to a landings obligation.We did not include the use of discard flexibilities of the LO (CFP Article 15, \cite{CFP2013}) or annaul quota swaps. We may thus have underestimated the flexibility of the fishery to respond to quota limitations imposed under both the landing obligation and exploiting at MSY \cite{Prellezo2016}. Achieving a balance between quota flexibility, over-exploitation risk, and administrative simplicity is critical for the profitability and sustainability of multi-species fisheries \cite{Alzorriz2018}. The success of any new regulation also depends on achieving a balance between the costs and benefits of measures that promote voluntary compliance and those that punish non-compliance. With poor enforcement the economic benefits of non-compliance outweigh the risks of detection \cite{Batsleer2013}. In this MSE framework, detection rates were assumed to be 100\% and fines were set sufficiently high so that no discarding occurred, reflecting full compliance with regulations. However, if detection rates are low and the short-term benefits of non-compliance are high (as our results suggest) then non-compliance is likely to be a substantial problem in the absence of measures promoting voluntary compliance.

>>>>

Meanwhile, when constraining both species, the production potential of both stocks was maintained, that is to say the yield curves were unchanged. The quota constraints were met by a reduction in fishing effort (Fig. \ref{f:effort}). as predicted in general terms by \cite{Ulrich2017}. This led to a reduction in fishing cost and an increase in net revenue over the mid-term because biomasses and yields increased. However, individual quota cobined with the stochastic fisheries catches resulted in lower than intended exploitation rates. The TACs were set so that the total TACs corresponded to the harvest rate that resulted in maximum sustainable yields. The TACs were divided in individual quotas for each fishing vessel. The lower than intended harvest rates were caused by the fact that despite their planning, fishers often exhausted one of the quotas before the other. If discarding is not allowed, then individual fishers must then stop fishing. At the population levels of the two species this resulted in overal cacthes that were lower than the TACs. Such lack of achieving MSY in mixed fisheries with multiple single-species quota has been described elsewhere \cite{Kempf2016, Rindorf2017, Hilborn2015}, but is generally attributed to differences in life-histories among fished species. In this study, the discrepancy between the intended annual quotas at MSY and realized catches is caused only by schochasticity in the system. This stochasticy in catch rates is observed in most fisheries \cite{Sampson1988, VanOostenbrugge2004, Smith1980, Bernasconi2015}. It is caused by the complex migration biology and the effects of environmental factors on fish behaviour. A well-functioning quota market would allow vessels to swap excess quota for constraining and thus bring realized catches closer to quotas.

In the case study explored here, setting quotas based on MSY for all species resulted in mixed fisheries that were economically more viable in the long run compared to the unconstrained cased. It should be noted that this particular result may not hold true for mixed fisheries with unavoidable catches or bycatches of very low productive species. Fishing those species at their MSY levels would probably constrain effort to such an extent that the net revenue will be reduced in the long-term \cite{Prellezo2016a,  Rindorf2017}.

The model aimed to evaluate the biological and economic effects of adopting a major policy change such as the CFP \cite{CFP2013}. Starting from an overfished mixed fishery under open access conditions but with a landing obligation, the response of individual effort allocation and the interannual population dynamics are explicitly modelled, while adopting MSY objectives. The analysis extended earlier approaches that used short-term state-dependent decision-making models (e.g. \cite{Alzorriz2018, Batsleer2016, Poos2010}) by including interannual population dynamics of fish stocks, and a management procedure that mimics the decisions of a management system. Such an MSE framework was thought of as a minimum realistic model \cite{Kell2007, Punt1995}. To keep the outcomes of the model simple, and to show the implications of the fishing effort allocation, the two fish populations modelled here are exactly the same apart from their spatial distribution difference (Fig. \ref{f:distribution}). As a result, if the landing obligation changes selectivity patterns in the short-term as predicted in \cite{Alzorriz2018, Batsleer2016}, the present MSE modeling approach allows the evaluation on the reference points for sustainable exploitation in longer terms by explicitly modelling how changes in exploitation rates impact fish populations and yields.

The forecasted effects of fisheries management in mixed fisheries result from spatial heterogeneity in resources and fishers adaptive behaviour. This emphasizes that human behaviour and decision-making are intrinsic parts of conservation and natural resource management and the need for incorporating detailed fishing dynamics in management strategy evaluation. Historically, the focus of management strategy evaluation has been primarily on population dynamics in single and multispecies fisheries \cite{Butterworth2007, Dichmont2006b, Punt1999, Punt2009, Smith1999, Punt2016}. Explicitly incorporating direct effects of human behaviour of those who harvest stocks is equally important \cite{Fulton2011,Milner-Gulland2012, Link2017}, but relatively few studies have attempted this \cite{Andersen2010, Ono2018, Simons2015a}. Our MSE that links a dynamic state variable model for fisher behaviour to a multi-species age structured model provides an alternative to those approaches.

The complexity of adding fishers behaviour in a minimum realistic model of mixed fisheries in an MSE framework requires making several simplifying assumptions. The details and possible consequences of these assumptions have been discussed in eg. \cite{Alzorriz2018}, and include full compliance of fishers with the discarding policy, absence of a quota market, monthly choices on fishing, and a lack of interference competition among fishers. Also, the utility function only comprises of decisions based on annual net revenues, omitting any social dynamics or tradition. These social dynamics and traditions are potentially important \cite{Girardin2017, Schluter2012}, and could be incorporated in future applications. Important assumptions about the dynamics of the population dynamics included negligible natural mortality, constant recruitment, constant growth, and constant migration.

In the study, the fishes were not allowed to discard, complying to a landings obligation.We did not include the use of discard flexibilities of the LO (CFP Article 15, \cite{CFP2013}) or annual quota swaps. We may thus have underestimated the flexibility of the fishery to respond to quota limitations imposed under both the landing obligation and exploiting at MSY \cite{Prellezo2016}. Achieving a balance between quota flexibility, over-exploitation risk, and administrative simplicity is critical for the profitability and sustainability of multi-species fisheries \cite{Alzorriz2018}. The success of any new regulation also depends on achieving a balance between the costs and benefits of measures that promote voluntary compliance and those that punish non-compliance. With poor enforcement the economic benefits of non-compliance outweigh the risks of detection \cite{Batsleer2013}. In this MSE framework, detection rates were assumed to be 100\% and fines were set sufficiently high so that no discarding occurred, reflecting full compliance with regulations. However, if detection rates are low and the short-term benefits of non-compliance are high (as our results suggest) then non-compliance is likely to be a substantial problem in the absence of measures promoting voluntary compliance.
